Quantum Programming Interfaces for NP-complete problems

### 2017-05-16 papers/paper.tex
Adds bibliography

\begin{thebibliography}{9}
    \bibitem{x}
        Authors
        \textit{Title}
        Pub, Loc, Date
\end{thebibliography}

>>>>

\begin{thebibliography}{9}
    \bibitem{}
        Pakin, Scott
        \textit{Performing Fully Parallel Constraint Logic Programming on a Quantum Annealer}
        Cambridge University Press, 2017
    \bibitem{}
        Grover, Lok K.
        \textit{A fast quantum mechanical algorithm for database search}
        Proceedings of 28th Symp Theory of Computing, 1996
    \bibitem{}
        John Wright
        \textit{Lecture 4: Grover's Algorithm}
        Carnegie Mellon University, 2015
    \bibitem{}
        Arvind, V., Schuler, Rainer
        \textit{The Quantum Query Complexity of 0-1 Knapsack and Associated Claw Problems}
        Archiv, Accessed 2017
    \bibitem{}
        Dahl, E. D.
        \textit{Programming With the D-Wave: Map Coloring Problem}
        D-Wave systems, 2013
    \bibitem{}
        Ines Dutra
        \textit{Constraint Logic Programming: a short tutorial}
        University of Porto, 2010
    \bibitem{}
        Jordan, Stephen
        \textit{Quantum Algorithm Zoo}
        math.nist.gov/quantum/zoo, Accessed 2017
    \bibitem{}
        Booth, Michael, Reinhardt, Steven P., Roy, Aidan
        \textit{Partitioning Optimization Problems for Hybrid Classical/Quantum Execution}
        D-Wave systems, 2017
    \bibitem{}
        Hen, Itay, Young, A. P.
        \textit{Exponential Complexity of the Quantum Adiabatic Algorithm for certain Satisfiability Problems}
        Department of Physics, UC Santa Cruz, 2011
    \bibitem{}
        Mandra, Salvatore, Guerreschi, Gian Giacomo, Aspuru-Guzik, Alan
        \textit{Faster than Classical Algorithm for Dense Formulas of Exact Satisfiability and Occupation Problems}
        Harvard University, 2016
    \bibitem{}
        Ambainis, Andris
        \textit{Quantum Search Algorithms}
        Archiv, Accessed 2017

\end{thebibliography}
